---
title: "Supplementary Information"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```

## Density models

To determine the influence of habitat on both density and detectability, we fitted a set of hierarchical distance sampling model for each of the surveys performed using a half-normal detection function.
Specifically, for each survey, we fitted four models. 
First, a model in which we assumed that habitat influences both crab density and detectability 
A second and third model in which we assumed habitat to be a covariate of only density and detectability, respectively. 
Finally, a fourth model in which we assumed that habitat did not influence either density or detectability. 
Then, for each survey, we determined the relative performance of each of the four models using the Akaike Information Criteria (AIC). 
Specifically, we determined the difference between each model's AIC and the model with the smallest AIC (a metric known as ∆AIC)
We then calculated the median ∆AIC for each type of model and compared it to determine which of the four assumptions performed better overall. 

```{r}
bdam <- drake::readd(best_detectability_abundance_model) %>%
  dplyr::mutate_if(is.numeric, round, digits = 1)
```

Our results indicate that habitat did not have an important effect on neither density or detectability. 
Indeed, we found that the fourth type of model (in which we assume no effect of habitat in neither density or detectability) had a median ∆AIC of `r bdam$median[bdam$model == "abu3"]` (min. `r bdam$min[bdam$model == "abu3"]`; max. `r bdam$max[bdam$model == "abu3"]`). 
In contrast, the first model set (in which we assume an effect of habitat on both density and detectability) had a median ∆AIC of `r bdam$median[bdam$model == "abu0"]`.

## Model outputs

Below the output of each of the models used in the paper

### Count models

```{r}
drake::loadd(count_models)
```


### Female crabs

```{r}
summary(count_models[[1]][[1]])
```

### Male crabs


```{r}
summary(count_models[[1]][[2]])
```

### Sex-ratio model

```{r}
summary(drake::readd(sex_ratio_models)[[1]])
```

### Size models

```{r}
drake::loadd(size_models)
```

## Female crabs

```{r}
summary(size_models[[1]][[1]])
```

## Male crabs

```{r}
summary(size_models[[1]][[2]])
```
